Describe and Explore: Using feature-based time-series clustering to understand modern intensive longitudinal data (Working Title)

### 2022-11-30 methods-and-results.Rmd
:bug:

```{r descrLong, include=FALSE}
# Sample Descriptives Table --- longer version
allMlCor %>%
  as.data.frame %>%
  kbl(.,
      format = "latex",
      caption = "Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_classic() %>%
  # add_header_above(
  #   .,
  #   c(
  #     "",
  #     "Correlations" = ncol(allMlCor),
  #     "Descriptives" = nrow(allMlCor) - ncol(allMlCor)
  #   )
  # ) %>%
  pack_rows("Correlations", 1, ncol(allMlCor)) %>%
  pack_rows("Descriptives", ncol(allMlCor)+1, nrow(allMlCor)) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{sidewaystable}\n\\centering", ., fixed = TRUE) %>%
  gsub("\\end{table}", "\\end{sidewaystable}", ., fixed = TRUE) %>%
  save_kable("Tables/descrWide.tex")
```

>>>>

```{r descrLong, include=FALSE}
# Sample Descriptives Table --- longer version
allMlCor %>%
  as.data.frame %>%
  kbl(.,
      format = "latex",
      caption = "Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1)),
      col.names = c(
        #"",
        "Int: \n Accidental", 
        "Int: \\newline Voluntary", 
        "Int: \n Cooperative",
        "Int: \n Representative",
        "Int: \n Meaningful",
        "Int: \n Quality", 
        "Core Need", 
        "Core Need \n Due to Partner", 
        "Attitude \n Partner",
        "Daytime \n Core Need",
        "Outgroup \n Attitude",
        "Well-being"
      )) %>%
  kable_classic() %>%
  pack_rows("Correlations", 1, ncol(allMlCor)) %>%
  pack_rows("Descriptives", ncol(allMlCor)+1, nrow(allMlCor)) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{sidewaystable}\n\\centering", ., fixed = TRUE) %>%
  gsub("\\end{table}", "\\end{sidewaystable}", ., fixed = TRUE) %>%
  save_kable("Tables/descrLong.tex")
```
